---
title: "GF_R_data"
output: html_document
date: "2024-08-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Convert Spec to Color and stats
# After you install the packages, load them using the library function
#install.packages("tidyverse")
#install.packages("magick")
#install.packages("pavo")

library(tidyverse)
library(magick)
library(pavo)

# Read in data (make sure you are in the correct working directory)
df = read.csv("~/Downloads/GF_data copy.csv", skip = 4)
```

```{r}
# Clean up the column names
# Extracting numbers from column names with X and number
new_names <- gsub("X([0-9]+)", "\\1", names(df))  
names(df) <- new_names

# Get only spectra and first column
spec_dat = df[,c(1,which(colnames(df)==350):which(colnames(df) == 1002))]

# Remove NA
spec_dat = na.omit(spec_dat)

# Clean up ID's (Removes anything after "_")
# (note, strsplit is a function from the tidyverse package)
ids = sapply(strsplit(spec_dat$name, "_"), function(x) x[1])

# Remove ID's and transpose matrix for pavo format 
spec_pavo = t(spec_dat[,-c(1)])

# Rename Columns
colnames(spec_pavo) = ids

# if its under 380, then its zero (for inside only, since there is no UV)
row.names(spec_pavo) # To check wavelength
spec_pavo[1:8,1:ncol(spec_pavo)] <- 0

# Add wavelength column for pavo
wl = as.numeric(rownames(spec_pavo))
spec_pavo = data.frame(wl, spec_pavo)
colnames(spec_pavo) = c("wl", ids)
#spec_pavo = spec_pavo[,2:ncol(spec_pavo)]
```
```{r}
########
#everything above is related to formatting csv to pavo in r 
# Convert to an rspec object
spec_format = as.rspec(spec_pavo, lim = c(350, 1000), exceed.range = T)
spec_format_for_color = as.rspec(spec_pavo, lim = c(300, 700), exceed.range = T)
#^to plot correct colors


# Fix negative values
spec_format = procspec(spec_format, fixneg = "zero")
spec_format[,2:ncol(spec_format)] <- spec_format[,2:ncol(spec_format)]*100
#takes numbers, multiplies by 100

# Fix negative values for color
spec_format_for_color = procspec(spec_format_for_color, fixneg = "zero")
spec_format_for_color[,2:ncol(spec_format_for_color)] <- spec_format_for_color[,2:ncol(spec_format_for_color)]*100

plot(spec_format, col = spec2rgb(spec_format_for_color), 
     type = "overlay", xlim = c(350, 1000))

#stuff below is just showing how colors are labeled
yeah <- spec2rgb(spec_format_for_color)
yeah

plot(spec_format, col= yeah, xlim=c(350, 700), lwd=4)
##

summary_stats = summary(spec_format)
summary_stats
```

# Saving using R scripts
write.csv(x = summary_stats, file = "Downloads/summary_for_practice.csv", row.names = T)

# Saving a figure
# Creates tiff file
tiff(filename = "~/Downloads/practice_fish_tiff.tiff",
     width = 10, height = 10, units = "cm", compression = "lzw", res = 300)
# Added to tiff file
plot(spec_format, col = spec2rgb(spec_format_for_color), 
     type = "overlay", xlim = c(350, 1000), lwd = 3)
# Closes tiff file
dev.off()

# Saving a pdf figure
# Creates pdf file
pdf(file = "~/Downloads/fish_spec.pdf", width = 7, height = 5)
# Added to pdf
plot(spec_format, col = spec2rgb(spec_format_for_color), 
     type = "overlay", xlim = c(350, 1000), lwd = 3)
plot(spec_format, col = spec2rgb(spec_format_for_color), 
     type = "overlay", xlim = c(350, 1000), lwd = 1)
# Closes pdf file
dev.off()







```

